---
title: "Lecture1"
author: "Uzair Mirza"
date: "06/05/2021"
output: pdf_document
---

## tidyverse Package used
```{r, include=F}
library(tidyverse)
```

 
### Simulation Example          slide 26/36
a) Topic: Height x Sprint time(100m)
b) Independent variable(x) = Height, dependent variable(y) = Sprint time(100m)
```{r}
## set the seed to have reusable results
set.seed(6969)

## now run simulation and generate the samples
    # for both height and Sprint time(100m) we can use runif() set a min/max 
    # height and Sprint time(100m) with round()
# height in format XXX.XX
height <- runif(10, 145, 185) %>% round(digits = 2)

# sprint times in format XX.XX
sprint_time <- runif(10, 20, 40) %>% round(digits = 2)

# now make a data frame of the results
data.1 <- tibble(height = height, sprint_time = sprint_time)
data.1
```
To simulate a diff sample, change the seed or remove the set.seed() to get a new sample on each run


### Breakout Group Example       slide 30/36
Declare and assign individuals to one of the 2 groups.
I used sample() with replacement because I made the Placebo and Treatment into a binary group and made them in a vector, to keep it fair sample() by default assigns equal prob to each outcome hence chances for choosing treatment and placebo for each member will be equal.
```{r}
## set the seed to have reusable results
set.seed(6969)

# assign RV to the 4 ppl in the group from 1-4
group <- c(1:4)

# declaring the treatment and placebo group.
  # Treatment = 1, Placebo = 0
test.1 <- c(0,1)

# generate samples to assign to each member in the group
pre.data1 <- sample(test.1, 4, replace = TRUE)

# now make a data frame
data.2 <- tibble(Subject = group, Treatment_Recieved = pre.data1)
data.2
```
Using runif() to generate the similar outcome.
I *expect* to not get the same result as the sample() but lets see.
```{r}
## set the seed to have reusable results
set.seed(6969)

# generate samples to assign to each member in the group.
  # here would have to use round to get the result in binary as runif() would not
  # include the extremes ie. min, max
pre.data2 <- runif(4, min = 0, max = 1) %>% round(digits = 0)

# now make a data frame
data.3 <- tibble(Subject = group, Treatment_Recieved = pre.data2)
data.3
```
as expected we did not recieve the same result as sample() is distributed discretely with each outcome given equal prob and runif() is distributed continuously(uniform distribution).


### Example                   slide 34/36
find sd
### R
```{r}
ages <- c(20,21,19,20,20,20,20)
sd(ages)
```
#### Manually
$\sigma^2_{y} = \frac{1}{N-1}\Sigma(y_{i}-\mu_{y})^2 \\$
$N = 7 \\$ 
$\mu_{y} = \frac{1}{N}\Sigma y_{i} = \frac{1}{7}*140 = 20 \\$
$\sigma^2_{y} = \frac{1}{6}\Sigma(y_{i}-20)^2 = \frac{1}{6} *2 = \frac{1}{3} =0.3333\\$ 


find sd
### R
```{r}
GTA <- c(1,1,1,1,0,0,0,0,0,0)
sd(GTA)
```

#### Manually
$\sigma^2_{y} = \frac{N}{N-1}P(1-P) \\$
$N = 10, P = \frac{4}{10} \Longrightarrow \sigma^2_{y} = \frac{10}{9}0.4(0.6)  = 0.2667 \\$

### Reason for difference in R vs Manual calculations
The reason for difference is because in R the sd() is the sample sd not the population sd.