---
title: "W3 Baysian Regression Model(BRM)"
author: "Uzair Mirza"
date: "20/05/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(brms)
library(tidyverse)
```

Setting up the data and making the plots
```{r}
# Data setup
blockXspeed <- tibble(blocks = c(3,4,5,6,7,10),
                      time = c(1,2,3,5,8,9))
# Making the scatter plot
    ## ALTERNATIVE CODE: From the data set make plot x = ??, y = ?? + type of the plot
ggplot(blockXspeed, aes(x=blocks, y=time )) + geom_point()

```
Now we setup the model using the brm() and look at the results
```{r}
# will be using the brm() for Baysian Regression
  # we declare our model equation uder formula, in the brm(formula = ?~?, data = ?, seed = ?)
  # Setup of the model is similar to the normal regression y ~ xi + (xj)^2 + ....
model <- brm(formula = time~blocks, data = blockXspeed, seed=69)

# use the standanrd summary to look at the regression results
summary(model)
```
Some interpratation of the output from the model:
1st we have the regular $\hat\beta_{0}$ and $\hat\beta_{i}$ and they have the regular regression interpratation.
The other thing is that the "Rhat" we **need** the Rhat value needs to be close to 1, if it is not 1 then we have a problem and we need to ....

                      **FILL DESCRIPTION OF PROBLEM RELATED TO Rhat**

Now let us try the previous thing with categorical variables
```{r}
# make the data frame
                  # given you have a degree will you support liberal
poll <- tibble(
  phd = sample(x = c("yes", "no", "maybe"), prob = c(0.25,0.45,0.3), replace = T, size = 100),
  support_liberal = sample(x = c("yes", "no"), replace = T, size = 100)
)

# setup the model       
                                                    # ? is family the distribution of the response, Yes Binary values
                                                    
model.2 <- brm(formula = views ~ phd, data = poll,family = bernoulli(), seed = 69)

```

Interprating the output and making some plots of the model to test the reliability of the model          
```{r}
# the classic summary
summary(model.2)

## mcmc_plot()
            # Verify what this shows, interpratation of it
mcmc_plot(model.2)
            # Verify what this shows, interpratation of it
mcmc_plot(model.2, type = "hist")

# we want to make sure our model is converging, to do this we need to check using this plot
mcmc_plot(model.2, type = "trace")
      # the graph we receive from trace shows us how the mode is working out the solution, 
      # the ideal goal is to have the chains mixed and there are no diversions in between the chains
      # problem would be if there chain i is units above or below chain j for either of the 3 graphs.

# posterior plots with bayesplot              ## figure out what these are ad how to use them

```
        
              



